---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Environmental attitudes: natural language processing of social media posts

<!-- badges: start -->
<!-- badges: end -->

The goal of this hackathon session is to find out how we can use social media data to find peoples attitudes to different environmental challenges or aspects of nature.

I am hopeful that the work we do today can inform a peer reviewed paper on environmental attitudes and social media data.

## Installation

You can install and load the code for this hackathon session from [GitHub](https://github.com/nfox29/seasHackathon) with:

```{r install, eval = FALSE}
devtools::install_github("nfox29/seasHackathon")

library(seasHackathon)
```


## Getting data from Flickr
The first social media website we will look at is Flickr.

```{r afinn, eval = TRUE}
tidytext::get_sentiments("afinn")
```


```{r afinn_flickr, eval = FALSE}
#search flickr for posts containing the word "nature" in a give place and time
flickr_raw <- photo_search(mindate_taken = "2022-01-01",
                           maxdate_taken = "2021-01-01",
                           bbox = "-134.648443,21.398553,-54.140630,49.925909",
                           text = "nature")

#here we create a new column called text and paste in all the other text from that row
flickr_raw$text <- paste2(flickr_raw$title,
                          flickr_raw$description,
                          flickr_raw$tags)

#use our custom function to add afinn sentiments to the
flickr_afinn <- get_afinn(flickr_data = flickr_raw)
```
